---
title: "<h1 style='text-align:center;'> Descriptive analysis </h1>"
author: "Hugo Marthinet"
date: "`r Sys.Date()`"
output:
  knitr:::html_vignette:
  toc: true
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Descriptive analysis}
  %\usepackage[utf8]{inputenc}
---

\setmainfont{Calibri Light}

```{r, echo = FALSE, message = FALSE}

# If you want to create a PDF document paste the following after line 9 above:
#   pdf_document:
#     toc: true
#     highlight: tango
#     number_sections: no
#     latex_engine: xelatex    
# header-includes: 
#    - \usepackage{fontspec}

knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library(dataDesc)
```

The goal of this packages is solely to provide an easy way to compute a descriptive analysis up to publication standards. 
The calculations do not differ from the descriptive analysis provided by other packages such as **gtsummary** or **tableone**, 
the upside lies in a variety of layout parameters. 

## Univariate analysis

Basic descriptive analysis of the whole dataset can be conducted simple calling the **describe** function and providing the dataset as the only parameter :

```{r, message = FALSE}
describe(iris)
```

One can also select the columns to describe, and provide new labels :

```{r, message = FALSE}
describe(iris, vars = 1:2, label = c("Length", "Width"), lang = "en")
```

Other arguments mainly allow control over the layout :

```{r, message = FALSE}
describe(iris, vars = 1:2, label = c("Length", "Width"), lang = "en",
         merge.cols = FALSE, include.conf = FALSE)
```

## Bivariate analysis

Bivariate analysis can be easily computed using the **factor** parameter. Statistical testing will then be added to the descriptive table.

```{r, message = FALSE}
describe(iris, vars = 1:2, factor = 5, label = c("Length", "Width"), lang = "en",
         merge.cols = FALSE, include.conf = FALSE, include.test.name = TRUE)
```
